SAYCAM preprocessing analyses from bounding box outputs

### 2021-12-23 preprocessing/step5_preprocess_fullset_from_bb_outputs.Rmd
add modifications to goldset outputs to includde center detectinos

@@

save(all_gold_sample_frames_op, file = here::here('data/preprocessed_data_2021/',paste0('gold_sample_from_bbs_2021_',dataset_type,'.RData')))
```

>>>>

   gold_sample_op_center <- this_vid_data %>%
     filter(frame %in% frames_to_get$frame) %>%
     mutate(center_y = top + height/2, center_x = left + width/2) %>% # get center_x and y
     filter(center_y<(limit_upper) & center_x<(limit_upper) & center_y>(limit_lower) & center_x>(limit_lower)) %>%   # filter within parameters
     group_by(frame, child_id, vid_name) %>% # group at frame level first
     summarize(hand_detected_center = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected_center = sum(!is.na(mean_confidence[label=='face']))>0)

   gold_sample_op<- gold_sample_op %>%
      right_join(gold_sample_op_center)[1:]

@@

save(all_gold_sample_frames_op, file = here::here('data/preprocessed_data_2021/',paste0('gold_sample_from_bbs_2021_with_center',dataset_type,'.RData')))
```
